\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\usepackage[normalem]{ulem} % Avoid changing \emph behavior
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{enumitem} % For list formatting
\usepackage{hyperref} % For clickable links
\usepackage{setspace}
\vspace{-0.8em} % Adjust this value to control spacing

\name{Ansaf Muhammed P T} % Your name
\vspace{-0.8em} % Adjust this value to control spacing
    \vspace{-0.5em} % Adjust this value to control spacing

\address{+91 9074849016 \\ Trivandrum, India} % Will be @addresstwo (Line 3)
    \vspace{-0.5em} % Adjust this value to control spacing
    \vspace{-0.5em} % Adjust this value to control spacing

\address{\href{mailto:ansafdev01@gmail.com}{ansafdev01@gmail.com} \\ \href{https://www.linkedin.com/in/ansafmohdpt/}{linkedin.com/in/ansafmohdpt} \\ \href{https://ansafmohdpt.github.io}{ansafmohdpt.github.io}} % Will be @addressthree (Line 4)
\address{Backend Developer} % Will be @addressone (Line 2)

\begin{document}

%----------------------------------------------------------------------------------------
%    SUMMARY
%----------------------------------------------------------------------------------------
\vspace{-0.8em} % Adjust this value to control spacing
    \vspace{-0.5em} % Adjust this value to control spacing

\begin{rSection}{SUMMARY}
{Java backend engineer with 5+ years of experience delivering scalable services on Java~8+, Spring Boot, and MySQL---from architecture and deployment through production monitoring. Builds event-driven systems with Apache Kafka and RabbitMQ; leads engineering initiatives spanning enterprise SaaS rollouts, high-volume data migrations, and disciplined database change management.}
\end{rSection}
\vspace{-0.8em} % Adjust this value to control spacing

%----------------------------------------------------------------------------------------
%    SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabularx}{\linewidth}{@{}>{\bfseries}l @{\hspace{3.5ex}} >{\RaggedRight}X @{}}
\textbf{Core Competencies} & Java, Spring Boot, MySQL, Liquibase, Flyway, Maven, REST, \mbox{Microservices}, n8n \\
\textbf{Basic Knowledge} & JavaScript, Angular, Docker, Kubernetes, Python, AWS EC2 \& ECS, PostgreSQL \\
\textbf{Tools \& IDEs} & IntelliJ, Eclipse, Cursor/Antigravity, MySQL Workbench, DBeaver, VS Code, Postman, PuTTY \\
\textbf{Version Control} & Git, SVN \\
\textbf{Project Management} & Jira, Bitbucket, Confluence \\
\textbf{Soft Skills} & Problem Solving, Leadership, Public Speaking, Volunteering, Technical Aptitude \\
\end{tabularx}
\end{rSection}

%----------------------------------------------------------------------------------------
%    EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-0.5em} % Adjust this value to control spacing

\begin{rSection}{Experience}

\begin{rSubsection}{Daiviksoft Technologies}{Oct 2024 -- Present}{Java Developer}{Remote}
    \itemsep -0.4em
    \vspace{-0.5em} % Adjust this value to control spacing


    \item Led a team of four to build scalable backend services and automated workflows using Java and Spring Boot.
    \item Engineered an on-demand synchronization architecture for CDISC libraries, empowering users to clone, customize, and save tailored libraries natively.
    \item Designed a centralized, asynchronous audit logging framework powered by Spring AOP and Apache Kafka.
    \item Architected event-driven microservices to maximize performance, integrating Spring AI for intelligent automation.
\end{rSubsection}
\vspace{-0.4em} % Adjust this value to control spacing

\begin{rSubsection}{Hyreo Technology Solutions}{Aug 2022 -- Oct 2024}{Senior Software Engineer \& Team Lead}{Trivandrum, India}

    \itemsep -0.4em
    \vspace{-0.5em} % Adjust this value to control spacing


    \item Led cross-stack teams in deploying SaaS solutions for clients like Daimler Truck and Creative Synergies Group.
    \item Migrated 20GB+ production data and redesigned over 10 hierarchical data fields in MySQL within one month.
    \item Integrated Apache Superset dashboards with Jinja templating and developed KPI/risk identification frameworks.
    \item Streamlined database change management by introducing Liquibase and optimized microservices with RabbitMQ.
    \item Promoted to Team Lead within a short tenure for demonstrated technical expertise and leadership.
\end{rSubsection}
\vspace{-0.4em} % Adjust this value to control spacing

\begin{rSubsection}{Flytxt Mobile Solutions}{Jan 2021 -- Jul 2022}{Software Engineer}{Trivandrum, India}
    \itemsep -0.4em
    \vspace{-0.5em} % Adjust this value to control spacing


    \item Contributed to a cloud-based SaaS product on AWS Elastic Cloud utilizing a microservice architecture.
    \item Developed front-end components using PolymerJS and integrated Razorpay payment gateway into Angular systems.
    \item Enhanced internal product monitoring tools and health endpoints for improved system observability.
\end{rSubsection}

\end{rSection}
\vspace{-1.0em} % Adjust this value to control spacing

%----------------------------------------------------------------------------------------
%    PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{Spring AOP Audit Logging Framework}{}{Daiviksoft Technologies}{}
    \itemsep -0.4em
    \vspace{-0.5em} % Adjust this value to control spacing


    \item Designed a centralized, asynchronous audit logging framework built on Spring AOP and Apache Kafka.
    \item Engineered the mechanism as a plug-and-play library for seamless integration with any Spring Boot application.
\end{rSubsection}
\vspace{-0.4em} % Adjust this value to control spacing

\begin{rSubsection}{Data Architecture \& Advanced Reporting}{}{Hyreo Technology Solutions}{}
    \itemsep -0.4em
    \vspace{-0.5em} % Adjust this value to control spacing


    \item Designed a new data storage architecture using MySQL and Spring Boot for complex hierarchical data mappings.
    \item Led the integration of Apache Superset dashboards using Jinja and SQL for advanced real-time reporting.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%    CERTIFICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}
\begin{itemize}
    \itemsep -0.3em
    \item Java Foundations \hfill {JetBrains}
    \item Git Essential Training \hfill {LinkedIn}
    \item Generative AI Essentials \hfill {Microsoft}
    \item Spring Boot 3 Essential Training \hfill {LinkedIn}
    \item SQL (Advanced) \hfill {HackerRank}
    \item AWS Route53: Routing Policies \hfill {Coursera}
    \item Java Object-Oriented Programming \hfill {LinkedIn}
    \item MySQL Explorer Badge \hfill {Oracle}
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%    EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Bachelor of Technology in Information Technology}, Government Engineering College, Trivandrum \hfill {2020}\\
{Grade: CGPA: 7.08}
\end{rSection}

%----------------------------------------------------------------------------------------
%    ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}
\begin{itemize}
    \itemsep -0.3em
    \item Awarded Best Employee of the Month within the first quarter of joining Hyreo.
    \item Successfully led 2+ customer rollouts and assisted 5+ others within one year globally.
    \item Streamlined database migrations using Liquibase, enhancing deployment reliability and efficiency.
    \item Elected as Secretary of the College-Level Student Organization (2019-2020).
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%    LANGUAGES
%----------------------------------------------------------------------------------------
\begin{rSection}{Languages}
\begin{itemize}
    \itemsep -0.3em
    \item English \hfill {Full professional proficiency}
    \item Malayalam \hfill {Native or bilingual proficiency}
    \item Hindi \hfill {Elementary proficiency}
\end{itemize}
\end{rSection}

\end{document}
